---
title: "Hw03"
author: "Xinyao Fan"
date: '2017-09-28'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(gapminder)
library(tidyverse)
```
## Task Menu

**Q1**
Get the maximum and minimum of GDP per capita for all continents.

```{r}
out<-gapminder%>%
  group_by(continent)%>%
  summarise(max_gdpPercap=max(gdpPercap), min_gdpPercap=min(gdpPercap))
knitr::kable(out)
```

**Q2**
Look at the spread of GDP per capita within the continents.
```{r}
out1<-gapminder%>%
  group_by(continent)%>%
  summarise(sd(gdpPercap), IQR=quantile(gdpPercap,0.75)-quantile(gdpPercap,0.25))
knitr::kable(out1)
```

**Q3**
Compute a trimmed mean of life expectancy for different years. Or a weighted mean, weighting by population. Just try something other than the plain vanilla mean.<br>

*trimmed mean*
```{r}
out3<-gapminder%>%
  group_by(year)%>%
  summarise(mean_trim=mean(lifeExp,trim=0.2))
knitr::kable(out3)
```

*weighted mean*
```{r}
out4<-gapminder%>%
  group_by(continent)%>%
  summarise(weighted_mean=weighted.mean(lifeExp,pop))
knitr::kable(out4)
```

**Q4**
How is life expectancy changing over time on different continents?
```{r}
ggplot(gapminder, aes(year, lifeExp)) +
    facet_wrap(~ continent) +
    geom_point() +
    geom_smooth(se=FALSE, span=1, method="loess")
```
## Including P

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
