---
title: "hw10"
author: "Xinyao Fan"
date: "December 5, 2017"
output: github_document
---

```{r include=FALSE}
library(tidyverse)
library(magrittr)
library(purrr)
library(glue)
library(stringr)
library(rvest)
library(xml2)
library(ggplot2)
library(httr)
library(forcats)

```

## Scrape data from the website

I am interested in the 200 greatest women artists, so I try to download the data from the billboard website and then do some data analysis.
```{r}
my_url <- "https://www.billboard.com/charts/greatest-billboard-200-women-artists"
page_title <- read_html(my_url)
```

First, I extract the artist name,the rank and also the link for each artist from the website and put all the data into a dataframe. Use stringr package to set the right link for each singer.
```{r}
get_artist <- function(my_link) {
  my_link %>% 
    read_html() %>% 
    html_nodes(css = ".chart-row__artist") %>% 
    html_text() %>%
    str_trim(side = "both") %>% 
    return()
}

get_rank <- function(my_link) {
  my_link %>% 
    read_html() %>% 
    html_nodes(css = ".chart-row__current-week") %>% 
    html_text() %>% 
    return()
}
Artist <- get_artist(my_url)
rank <- get_rank(my_url)
df <- data_frame(rank = rank,
                 Artist = Artist,
            Link=glue("https://www.billboard.com/music/{Artist}")%>% 
                   str_to_lower() %>% 
                   str_replace_all(" ","-") %>% 
                   str_replace_all("&","") %>% 
                   str_replace_all("'","") %>% 
                   str_replace_all("--","-") %>% 
                   str_replace_all(",","") %>% 
                   str_replace_all("!",""))
```

However, I notice that the artist Mary J. Blige's link is not match wiht the artist name, so I try to replace the link with the correct one.
```{r}
df$Link[18] <- "https://www.billboard.com/music/mary-j-blige"
```

Next, I extracted the statistics nested in each artist's page: No1hit,Top10hits,songs and put all this information into a dataframe.

```{r}
get_stats <- function(link) {
  link %>% 
    read_html() %>% 
    html_nodes(css = ".artist-section--chart-history__stats__stat--number") %>% 
    html_text() %>% 
    return()
}
```

Use possibly to hand with the missing information.

```{r warning=FALSE}
get_stats_safe <- purrr::possibly(get_stats, "None available")

df <- df %>% 
  mutate(Stats = map(Link, get_stats_safe))
```

Since some artists don't have data of No1Hit and Top10Hits. So, we have to judge the length of the vector Stats. For the missing information,such as NO1Hit, Top10Hits, we replace the NA by "O".
```{r warning=FALSE}
No1Hits<-c()
Top10Hits<-c()
Songs<-c()

for (i in 1:50) {
	if(length(df$Stats[[i]])==3){
	No1Hits[i]<-df$Stats[[i]][1]
	Top10Hits[i]<-df$Stats[[i]][2]
	Songs[i]<-df$Stats[[i]][3]
	}else if(length(df$Stats[[i]])==2)
  { No1Hits[i]<-0
     Top10Hits[i]<-df$Stats[[i]][1]
    Songs[i]<-df$Stats[[i]][2]
	}else if(length(df$Stats[[i]])==1)
	{ 
		No1Hits[i]<-0
		Top10Hits[i]<-0
	  Songs[i]<-df$Stats[[i]][1]
	
	}
 
}

df_new<- data_frame(rank = rank,
                 Artist = Artist,
                 Link = glue("https://www.billboard.com/music/{Artist}") %>% 
                   str_to_lower() %>% 
                   str_replace_all(" ","-") %>% 
                   str_replace_all("&","") %>% 
                   str_replace_all("'","") %>% 
                   str_replace_all("--","-") %>% 
                   str_replace_all(",","") %>% 
                   str_replace_all("!",""),
                 No1Hits=as.numeric(No1Hits),
                 Top10Hits=as.numeric(Top10Hits),
                 Songs=as.numeric(Songs))
write_csv(df_new, "women_200.csv")
```

## Data Analysis
First, we give an overview of the distribution for Top 10 Hits in our data.
```{r}
ggplot(df_new, aes(Top10Hits))+geom_histogram()+
  ggtitle("Histogram of Top 10 Hits for greates 200 women") +
  theme(plot.title = element_text(hjust = 0.5))
```

Then, we filter the artists whose No.1 Hits songs>5 and look the detailed information. Arrange by # of No.1 Hits songs.
```{r}
out1<-df_new%>%
	filter(No1Hits>5)%>%
	select(rank,Artist,No1Hits,Top10Hits,Songs)%>%
  arrange(No1Hits)
knitr::kable(out1)
```

We found that Mariah Carey has the most No.1 Hit songs.
Now, for these singers, we arrange them by the number of their songs and give a plot.

```{r}
df_new%>% #use fac_order
  filter(No1Hits>5) %>%
  ggplot(aes(y=fct_reorder(Artist, Songs, max,.desc = TRUE),x=Songs)) + geom_point()+scale_y_discrete("artist_name")
```

Now, we want to explore the ratio of Top10 hits songs vs all the singer's songs and arrange them.
```{r}
out2<-df_new%>%
	mutate(prob=(-Top10Hits/Songs))%>%
	arrange(prob)%>%
	filter(abs(prob)>0.55)%>%
	select(rank,Artist,Top10Hits,Songs)%>%
	mutate(prob=Top10Hits/Songs)
knitr::kable(out2)
```

We could find that Destiney's child only have 14 songs, but 10 of them are the TOP10Hits songs!
