---
title: "Gapminder"
output: github_document 
---
##Load packages"tidyverse","gapminder"
```{r}
library(tidyverse)
library(gapminder)
```
##Display the structure of the dataset
```{r}
str(gapminder)
```
## Print the dataset to the screen
Since we use the library"tidyverse", only the important stuff will appear on the screen
```{r}
class(gapminder)
gapminder
```
##Display the head and tail of the dataset
```{r}
head(gapminder)
tail(gapminder)
```
## Query more basic information on a dataset 
```{r}
names(gapminder)
ncol(gapminder)
length(gapminder)
dim(gapminder)
nrow(gapminder)
```
## A statistical overview of the dataset
```{r}
summary(gapminder)
```
## A few figures
```{r}
plot(lifeExp ~ year, gapminder)
plot(lifeExp ~ gdpPercap, gapminder)
plot(lifeExp ~ log(gdpPercap), gapminder)
```
## Look at the variables inside the data frame
```{r}
head(gapminder$lifeExp)
summary(gapminder$lifeExp)
hist(gapminder$lifeExp)
#The year variable is an integer variable,
#but since there are so few unique values 
#it also functions a bit like a categorical variable
summary(gapminder$year)
table(gapminder$year)
#The variables for country and continent hold truly categorical information, which is stored as a factor in R.
class(gapminder$continent)
summary(gapminder$continent)
levels(gapminder$continent)
nlevels(gapminder$continent)
```
## ggplot of the dataset
```{r}
p <- ggplot(filter(gapminder, continent != "Oceania"),
            aes(x = gdpPercap, y = lifeExp)) # just initializes
p <- p + scale_x_log10() # log the x axis the right way
p + geom_point() # scatterplot
p + geom_point(aes(color = continent)) # map continent to color
p + geom_point(alpha = (1/3), size = 3) + geom_smooth(lwd = 3, se = FALSE)
p + geom_point(alpha = (1/3), size = 3) + facet_wrap(~ continent) +
  geom_smooth(lwd = 1.5, se = FALSE)
```
```
